Ce que j'ai compris jusqu'à maintenant\\Début de rapport ?

### 2025-05-13 article_bihom_v2.tex
fini regularité ?

		\begin{itemize}
			\item Let $\mathbb{F}$ be a finite field and $\mathbb{K}$ a field not necessarily finite. 
			\item We denote the multivariate polynomial ring defined over a field in $n$ variables $\mathbb{K}[x_1,\dots,x_n] = R$ where $n$ is a positive integer.
			\item We will use the standard notation for matrix multiplication complexity for a square matrix of size $n$, $\mathcal{O}(n^\omega)$,
			where $2 \leq \omega \leq 3$.
			\item Let $R_{\leq s}$ be the polynomials of total degree $\leq s$. $I_{\leq s} = I \cap R_{\leq s}$.
		\end{itemize}

@@

		\subsection{Hilbert series}
		Hilbert-Poincaré series (or just Hilbert series) is a very important tool in algebraic geometry to describe ideals and varieties and their dimensions.
		\begin{definition}[\cite{CLS}]
			Let $I$ be an ideal in $R$. The affine Hilbert function of $I$ is the function on the nonnegative integers s defined by
			$$
				{}^a HF_{R/I}(s) = dim R_{\leq s} / dim I_{\leq s} = dim R_{\leq s} - dim I_{\leq s}.
			$$
		\end{definition}

@@

		The smallest integer $s_0$ such that $HF_{R/I}(s_0) \leq 0$ is called the degree of regularity of the ideal $I$.

>>>>

		\begin{itemize}
			\item Let $\mathbb{F}$ be a finite field and $\mathbb{K}$ a field not necessarily finite. 
			\item We denote the multivariate polynomial ring defined over a field in $n$ variables $\mathbb{K}[x_1,\dots,x_n] = R$ where $n$ is a positive integer.
			\item We will use the standard notation for matrix multiplication complexity for a square matrix of size $n$, $\mathcal{O}(n^\omega)$,
			where $2 \leq \omega \leq 3$.
			\item Let $R_{s}$ be the polynomials of total degree $s$. $I_{s} = I \cap R_{s}$.
		\end{itemize}

@@

		\subsection{Hilbert series}
		Hilbert-Poincaré series (or just Hilbert series) is a very important tool in algebraic geometry to describe ideals and varieties and their dimensions.
		\begin{definition}[\cite{CLS}]
			Let $I$ be a homogeneous ideal in $R$. The affine Hilbert function of $I$ is the function on the nonnegative integers s defined by
			$$
				{}^a HF_{R/I}(s) = dim R_{s} / dim I_{s} = dim R_{s} - dim I_{s}.
			$$
		\end{definition}

@@

		The index of regularity is the smallest integer $s_0$ such that $HF_{R/I}(s_0)$ is equal to a certain polynomial called the Hilbert polynomial. We will denote $H(I)$ as the index or degree of regularity of I.
